### 2019-04-05 README.Rmd
Update vignette

head(cites_metadata())

@@

[![Created by EcoHealth Alliance](https://raw.githubusercontent.com/ecohealthalliance/citesdb/master/man/figures/eha-footer.png){data-external="1"}](https://www.ecohealthalliance.org/)

>>>>

```{r}
head(cites_metadata())

@@

[![Created by EcoHealth Alliance](https://raw.githubusercontent.com/ecohealthalliance/citesdb/master/vignettes/figures/eha-footer.png){data-external="1"}](https://www.ecohealthalliance.org/)
